Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-27 prop_iop.tex
Updating according to the meeting...
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

\begin{definition}\cite{RobertsVarberg1973,peres1995quantum,544199}Given
a operator or matrix\nb$\rho$, the norm of $\rho$ is defined by
\begin{equation}
\left\Vert \rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho}{\psi}\right|\,.
\end{equation}
\end{definition}

@@

For example, any pure state is not totally mixed, and $\mathbb{1}/3$
is a totally mixed over a three-dimensional Hilbert space.

@@

\begin{example}Given the additive interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$,
the maximum length of intervals in $\widehat{\mathscr{I}}_{n}$ is
$1/n$, and $\min_{x\in\left(0,1\right)}\left\{ \max\widehat{\iota}_{n}\left(x\right)-x,x-\min\widehat{\iota}_{n}\left(x\right)\right\} =1/\left(4n\right)$.
Therefore, for any totally mixed state\nb$\rho$ on a $d$-dimensional
Hilbert space, we have
\begin{itemize}
\item If $\left\Vert \rho-\rho'\right\Vert \le\left(4dn\right)^{-1}$, then
$\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
\item If $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
\end{itemize}
\end{example}

>>>>

\begin{definition}\cite{544199} Given a operator or matrix\nb$\rho$,
the norm of $\rho$ is defined by 
\begin{equation}
\left\Vert \rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho}{\psi}\right|\,.
\end{equation}
\footnote{Notice that it doesn't have square root, and this definition only
appears in \cite{544199}... Need to this definition in other sources.}\end{definition}

@@

For example, any pure state is not totally mixed, and $\mathbb{1}/3=\left(\proj{0}+\proj{1}+\proj{2}\right)/3$
is a totally mixed over a three-dimensional Hilbert space.

@@

\begin{example}Given the additive interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$,
the maximum length of intervals in $\widehat{\mathscr{I}}_{n}$ is
$1/n$, and $\min_{x\in\left(0,1\right)}\left\{ \max\widehat{\iota}_{n}\left(x\right)-x,x-\min\widehat{\iota}_{n}\left(x\right)\right\} =1/\left(4n\right)$.
Therefore, for any totally mixed state\nb$\rho$ on a $d$-dimensional
Hilbert space, we have
\begin{itemize}
\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(4dn\right)$, then
$\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
\item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
\end{itemize}
\end{example}
